Unifying the communicable disease spreading paradigm with Gompertzian growth

### 2022-05-27 PNAS/PNAS-main.tex
typos

% Please add here a significance statement to explain the relevance of your work
\significancestatement{
We seek to connect the communicable disease paradigm with the recently observed mortality patterns of the initial Coronavirus pandemic in March-April 2020 that have been shown by many to exhibit Gompertzian growth. In doing this, we show that this type of growth pattern is incompatible with traditional communicable disease spreading models, but rather with a model through which a ubiquitus and instanteneous stressor elicits a mutual stress response.
The findings of this paper call for a fundamental and interdisciplinary discussion of our accepted knowledge on communicable diseases, as the observations constitute a classic Kuhnian "anomaly" suggesting a paradigm shift away from that of a purely communicable disease paradigm to a hybrid where the environment plays a bigger role.}

>>>>

% Please add here a significance statement to explain the relevance of your work
\significancestatement{
We seek to connect the communicable disease paradigm with the recently observed mortality patterns of the initial Coronavirus pandemic in March-April 2020 that have been shown by many to exhibit Gompertzian growth. In doing this, we show that this type of growth pattern is incompatible with traditional communicable disease spreading models, but rather with a model through which a ubiquitous and instantaneous stressor elicits a mutual stress response.
The findings of this paper call for a fundamental and interdisciplinary discussion of our accepted knowledge on communicable diseases, as the observations constitute a classic Kuhnian "anomaly" suggesting a paradigm shift away from that of a purely communicable disease paradigm to a hybrid where the environment plays a bigger role.}
